Species persistence under climate and fishing

### 2014-01-10 Writing/MS.tex
small changes to methods

\begin{equation}
m_i=\int^{\frac{L}{2}}_{-\frac{L}{2}}b_i(y-c)f\left((1-h)\sum^\infty_{i=1}m_ia_i(x)\right)
dy. \label{recursive_m}
\end{equation}

@@

\noindent For each kernel, we can find the expected distance an offspring will travel, $\langle d \rangle$, which we will use to compare the two kernels.  For each kernel, the population's ability to persist depends on properties of the population itself: how far larvae 
tend to disperse ($\langle d \rangle$) and the intrinsic growth rate ($R_0$); properties of the environment: the 
length of the viable patch ($L$) and how quickly the environment is shifting ($c$); and the harvesting rate ($h
$). If the environment shifts more quickly than the critical rate $c^*$ or the population is harvested at more than 
the critical rate $h^*$ then the population will not be able to persist, as described in the Appendix.

>>>>

\begin{equation}
m_i=\int^{\frac{L}{2}}_{-\frac{L}{2}}b_i(y-c)f\left((1-h)\sum^\infty_{j=1}m_ja_j(x)\right)
dy. \label{recursive_m}
\end{equation}

@@

\noindent For each kernel, we can find the expected distance an offspring will travel, $\langle d \rangle$, which we will use to compare the two kernels.  For each kernel, the population's ability to persist depends on properties of the population itself: how far larvae 
tend to disperse ($\langle d \rangle$) and the intrinsic growth rate ($R_0$); properties of the environment: the 
length of the viable patch ($L$) and how quickly the environment is shifting ($c$); and the harvesting rate ($h
$). If the environment shifts more quickly than the critical rate $c^*$ or the population is harvested at more than 
the critical rate $h^*$ then the population will not be able to persist, as described in the Appendix.  For a Gaussian kernel, the critical rates $c^*$ and $h^*$ are those values of $c$ and $h$ such that 
$$R_0(1-h)2\sqrt{2}\exp\left(\frac{-c^2}{8D}\right)\left[\text{erf}\left(\frac{L-c}{2\sqrt{2D}}\right)-\text{erf}\left(\frac{-L-c}{2\sqrt{2D}}\right)\right]=1.$$
A similar expression for a sinusoidal kernel is derived in the appendix.  For both kernels, the critical harvesting proportion can be approximated by a function that looks like 
\begin{equation}
h^*\sim1- \frac{1}{R_0}\cdot C(L)f(\sigma^2,c^2,L^2+3c^2)
\end{equation}
where $C(L,R_0)$ is a decreasing function of the length of the viable patch and the intrinsic growth rate.
